---
title: "Literate Programming"
output: html_document
date: '2022-04-07'
---

##Introduction

[Literate Programming](https://en.wikipedia.org/wiki/Literate_programming) is a programming paradigm introduced by Donald Knuth in which a computer program is given an explanation of its logic in <span style="color: blue;">**natural language**</span>,such as English, interspersed with snippets of macros and traditional <span style="color: red;">**source code**</span>, from which compilable source code can be generated.

## Goal: Capture code, text/comments and output in a single document.

## M.V.P of Reproducibility (R Markdown)

- Output is self-documenting(code is embedded)
- Has to run sucessfully to save/knit output
- Is diffable & human readable in version control

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)


```


R has built in datasets for experimentation. To list the pre-loaded data, type the function **data()**:
```{r}
data()
```


For this example the Seatbelts data is used. First it is loaded and then it can be explored.
```{r}

#1. Load the data
data("Seatbelts")

# Print the first 6 rows
head(Seatbelts, 6)

```


Learn more about the Seatbelts data by typing the following:
```{r}
?Seatbelts

```


## Work with the pre-seatbelt period to identify a model, using logs
```{r}
work <- window(log10(UKDriverDeaths), end = 1982 + 11/12)
par(mfrow = c(3,1))
plot(work); acf(work); pacf(work)

```

```{r}
par(mfrow = c(1,1))
fit <- arima(work, c(1,0,0), seasonal = list(order = c(1,0,0)))
z <- predict(fit, n.ahead = 24)
ts.plot(log10(UKDriverDeaths), z$pred, z$pred + 2*z$se, z$pred - 2*z$se,
        lty = c(1,3,2,2), col = c("black", "red", "blue", "blue"))

```

```{r}
x <- Seatbelts[, c("kms", "PetrolPrice", "law")]
x[,1] <- log10(x[,1]) - 4
arima(log10(Seatbelts[, "drivers"]), c(1,0,0),
      seasonal = list(order = c(1,0,0)),
      xreg = x)
```


